A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-08-10 manuscript/paper_latex.Rmd
rename metric characterisation

```{r}
add_sfig(
  figure_file("edge_flip_comparison.tmp.pdf", experiment_id="03-metric_characterisation/4-edge_flip"), 
  "edge_flip_comparison", 
 "Edge flip score values for common trajectory topologies",
  ""
)
```

>>>>

```{r}
add_sfig(
  figure_file("edge_flip_comparison.tmp.pdf", experiment_id="02-metric_characterisation/4-edge_flip"), 
  "edge_flip_comparison", 
 "Edge flip score values for common trajectory topologies",
  ""
)
```
